Estimating Comparative Advantage in Improved Seed Adoption: Hybrid Maize in Ethiopia

### 2021-11-24 paper.tex
Updates from Overleaf

\usepackage{natbib}
\bibliographystyle{rusnat}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{caption}

@@

The ESS has has both self-reported

% Explain summary stats
% different definitions of yields
% hybrid and trajectories

@@

Our base analysis will be inspired by the work of \citep{Suri2011-oi}. This estimation framework imposes a parametric relationship between farmers' absolute advantage (i.e., the component of productivity that is independent of technology) and their comparative advantage (i.e., their relative productivity of adopting the improved technology over not adopting). This method seeks to estimate the following equation:

$$
yit=+ hit + i+ihit + i+it
$$

>>>>

\usepackage{natbib}
\bibliographystyle{rusnat}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{amsmath}

@@

The ESS has has both self-reported and crop cut yields available. This provides two sources of yield information, although self-reported yields seem to be overly large compared to either fresh or dried crop cut yields. Self-reported yields are both more susceptible to behavioral biases, but also to confusion caused by differences in assumed units. In general, though, the sample with available yield information cuts down the available sample immensely, which limits the power of the estimation. It isn't clear whether unavailable yields numbers is due to some sort of selection or whether crop cuts were only collected randomly from a few households.

@@

The advantage of our estimation strategy is that we do not rely on identification from an instrument or the structure of a model, but from the fact that the trajectory that a household takes in their adoption decisions through time is an informative source of identifying information. See \cite{Tjernstrom_Emilia_Dalia_Ghanem_Oscar_Barriga_Cabanillas_Travis_J_Lybbert_Jeffrey_D_Michler_and_Aleksandr_Michuda2020-bc} for more information on the assumptions involved for the Group Random Coefficients estimator. Table \ref{tbl:trajectories} maps out the

This method seeks to estimate the following equation:

\begin{align}
y_{it}&=\sum_{\underline{h}\in\mathcal{H}\backslash (1,1)}\mu_{\underline{h}}1\{h_{i}=\underline{h}\}+\sum_{\underline{h}\in\mathcal{H}_{S}}\Delta_{\underline{h}}h_{it}1\{h_{i}=\underline{h}\}+\kappa_{(1,1)}h_{it}1\{\underline{h}=(1,1)\}+\epsilon_{it}.\label{eq:GRC}
\end{align}
